---
title: "Dashboard Mock-Up"
author: "Yuval Vizan"
date: "`r Sys.Date()`"
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.dim = c(11,4))
source(file = "analysis_script.R")
source(file = "challenges_analysis.R")
source(file = "optimization_script.R")
```


# {.tabset}  

## Date Overview & Exploration  

**You are responsible for providing leadership with insights into Intuit's ability to protect its customers.**    
**Suggest several metrics that will provide insights into the data. Include a clear definition and rationale for each one.**    
**Create a mock-up of a dashboard that displays how these metrics change over time.**   
**Based on your findings, what insights would you share with your leadership?**     


* ~2300 logins per month (~50% of those are fraud)  
* all non-fraud log-ins are part of related to the same product category 'Other'  
* 

### Logins Volume {.tabset}  



```{r, results='asis', message=FALSE, warning=FALSE}
pad_html("Monthly", 4)
login_cnt_over_time$monthly_fig
login_cnt_over_time$monthly_fig_by_cat

pad_html("Weekly", 4)
login_cnt_over_time$weekly_fig
login_cnt_over_time$weekly_fig_by_cat

```

### General Exploration {.tabset} 

```{r, results='asis', message=FALSE, warning=FALSE}
pad_html("Account Status", 4)
profile_status_plot
pad_html("Device Status", 4)
new_device_sahre_plot
new_device_sahre_overtime_plot

pad_html("Session Time", 4)
pad_html("**Fraudulent logins tend to have a much longer session time**")
session_time_summary %>% 
  mutate(across(.cols = c(avg_session_time, median_session_time, max_session_time), .fns = ~round(.x, 1))) %>% 
  create_rmd_table_2(caption = "Measured In Minutes", col_to_factor = 1, col_to_comma = c(6))
session_length_density

pad_html("Score Distribution by Fraud Status", 4)
pad_html("* Significant amount of scores is missing from the non-fraud login population - but model fraud separation is still very convincing")
score_nas %>%
  create_rmd_table_2(col_to_factor = 1, col_to_comma = c(2, 3), col_to_percent = 4)
score_distribution

pad_html("Challenges Data", 4)
  pad_html("How many logins are challenged at all?", 5)
  knitr::opts_chunk$set(echo = FALSE, fig.dim = c(11,6))
  pad_html("* While steady (high) for new devices, challenge rate for existing devices goes way up mid april - I think this is related to population composition change in mid April post tax season")
  any_challenge_rate

  pad_html("How are customer challenged?", 5)
  pad_html("* good logins are mostly challenged with pswd, and unproportionally failing at Email & SMS")
  pad_html("* fraud logins are unproportionally failing at Voice challenge but its a small group - consider using this more?")
  challenge_type_distribution$overall
  challenge_type_distribution$failed_nonfailed_comparison
  
  pad_html("Failure Rate over time", 5)
  pad_html("* good customer failure rate drops mid April (Tax season?) - this is mostly coming from SMS & pswd challenges")
  fail_rate_over_time_figs$failed_anything
  fail_rate_over_time_figs$fail_rate_specific
  
  pad_html("Not very intersting", 5)
  challenge_type_over_time

pad_html("Account Age", 4)
account_age_density

pad_html("Login Hour Distribution", 4)
login_hour_distribution

pad_html("Maturation")
maturation_fig

```

## Dashboard Mock-Up  

### KPIs Overview  

```{r, results='asis', message=FALSE, warning=FALSE}
kpi_overview %>% 
  create_rmd_table_2(col_to_comma = c(1:3), col_to_percent = c(4:7), other_extensions = NULL)

kpi_by_prod %>% 
  create_rmd_table_2(col_to_comma = c(2:4), col_to_percent = c(5:8), other_extensions = NULL, caption = "By Product")
```


### KPIs Over Time {.tabset} 


```{r, results='asis', message=FALSE, warning=FALSE, fig.dim = c(13,3)}
pad_html("Monthly", 4)
kpis_over_time_plots$confirmd_fraud_rate_monthly
kpis_over_time_plots$fraud_coverage_monthly
kpis_over_time_plots$insult_rate_monthly
pad_html("Weekly", 4)
pad_html("Something  clearly changes in mid April - Fraud Rate goes up at the same time as Login completion rate goes down - I think this is related to TT seasonality")
kpis_over_time_plots$confirmd_fraud_rate_weekly
kpis_over_time_plots$fraud_coverage_weekly
kpis_over_time_plots$insult_rate_weekly
```

### Can we protect our customers?   

```{r}
tradeoff_plt
kpis_over_time_opt

ggplotly(tst_segment3, tooltip = "text")
```


## Insights??   

* Due to the fraud level in new devices logins - my recommendation is to improve verification protocols for new devices   
* optimization simulation can go in here    
* increase usage of voice challenges for new devices


## Notes 

### Fraud Insights: 

* see more fraud on the extrems of account age - both young and old   

fraud logins are failing pswd, if failed pswd -> voice challenge
legit users are succeeding pswd challeng, but dont love email/SMS 

### Discrepancies: 

* non unique login IDs  
* 71% of the unsuccessful logins have NULL model_score  


### To Me: 

* model separate fraud really well, simulate performance with arbitrary TH  
* same session, same device, all logins (3) are fraud on the same day, very quick session time
* only 3 unique case IDs  
* I see some in-week seasonality



